Lattice Boltzmann study of mass transfer for Bretherton/Taylor bubble train flow

### 2012-02-18 Text/introduction.tex
Van Baten works :)
Need to work on the paper.

\title{Lattice Boltzmann study of mass transfer for complicated geometries}

\begin{document}
\maketitle
\begin{abstract}
This work presents a thorough procedure of how to determine the volumetric mass transfer
coefficient
in the context of lattice Boltzmann simulations. The novelty of this work lies in the establishing
a thorough procedure of how to measure the volumetric mass transfer coefficient in case of mass
sources to be comparable of the representative unit cell, which accounts for the inhomogenous
situation. The strategies of how to speed up simulations, what the boundaries conditions are
thoroughly examined. Overall, all methods are consistent between each other as soon as the averaged
domain concentration is taken as the characteristic concentration. Though more difficult to setup
simulations with a few unit cells can give additional information about how well the liquid slug is
mixed. The work is of use to people performing mass transfer numerical simulations within the
lattice Boltzmann context.
\end{abstract}

@@

If one can assume that the mass point sources are distributed in the whole medium, then the mass accumulated in the unit volume $V=A \Delta x$ can be calculated as the difference of 
mass fluxes entering and leaving domain $U \bigl(C(x+\Delta x)-C(x)\bigr)$. We assume that the
source is a point source with the effective perimeter (area) $P$. The accumulated mass should be proportional
to the mass transfer coefficient:
\beq
U \bigl(C(x+\Delta x)-C(x)\bigr)=k_L P \bigl(\cstar-C(x)\bigr), 
\feq 
giving the same equation but only in the coordinate domain:
\beq
\label{concentration:domain:coordinate}
C(x)= \cstar \Bigl(1-\exp\bigl(-k_L a \frac{x}{U} \bigr)\Bigr).
\label{main:mass:transfer:expression} 
\feq

>>>>

\title{Lattice Boltzmann study of mass transfer for Bretherton/Taylor bubble train flow}

\begin{document}
\maketitle
\begin{abstract}
This work presents a thorough procedure of how to determine the volumetric mass transfer
coefficient
in the context of lattice Boltzmann simulations for Bretherton/Taylor bubble train motion. The
novelty of this work lies in the establishing
a thorough procedure of how to measure the volumetric mass transfer coefficient depending on the
capillary number $Ca$ regime. For example, for $Ca<0.7$ the flow has a vortex in front of the
bubble, but for the larger capillary number it hasn't. In case of mass
sources to be comparable of the representative unit cell (inhomogenous
situation), one cannot estimate  the strategies to measure the volumetric mass transfer coefficient
are presented. The strategies of how to speed up simulations, what the boundaries conditions are
thoroughly examined. Overall, all methods are consistent between each other as soon as the averaged
domain concentration is taken as the characteristic concentration. Though more difficult to setup
simulations with a few unit cells can give additional information about how well the liquid slug is
mixed. The work is of use to people performing mass transfer numerical simulations within the
lattice Boltzmann context.
\end{abstract}

@@

If one can assume that the mass point sources are distributed in the whole medium, then the mass accumulated in the unit volume $V=A \Delta x$ can be calculated as the difference of 
mass fluxes entering and leaving domain $U \bigl(C(x+\Delta x)-C(x)\bigr)$. We assume that the
source is a point source with the effective perimeter (area) $P$. The accumulated mass should be proportional
to the mass transfer coefficient:
\beq
U \bigl(C(x+\Delta x)-C(x)\bigr)=k_L P \bigl(\cstar-C(x)\bigr), 
\feq 
giving the same equation but only in the coordinate domain:
\beq
%\label{concentration:domain:coordinate}
C(x)= \cstar \Bigl(1-\exp\bigl(-k_L a \frac{x}{U} \bigr)\Bigr).
\label{main:mass:transfer:expression} 
\feq
